---
title: "Part 2 MLP"
author: "Shaaf Ahmad W17906977"
date: '2022-04-29'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

## Discussion of the various methods used for defining the input vector

Time series is a dataset in which one or more variables are measured over time. We will be doing a One-step forecast using the Autoregression (AR) model. AR is a linear model which predicts a variables future value using its past (lag) values.

However there are other models which can be used in time series forecasting. 

#### Moving Average (MA)

Moving average models use lagged values of forecast errors. The moving average model has use multiple steps back. MA(3) model has an order of 3 and uses 3 time step back.

#### Autoregressive moving average (ARMA)

ARMA models combine both Autoregression and Moving average into one model. ARMA uses both values of past forecast errors and past lag values. This model is often known as ARMA(p,q) model where p is p lagged values and q is the residuals up to q lags.

#### Autoregressive integrated moving average (ARIMA)

ARIMA(p,d,q)


#### Seasonal autoregressive integrated moving-average (SARIMA)

<br/>
<br/>
<br/>
<br/>

```{r}
library(readxl)
library(neuralnet)
library(grid)
library(MASS)
library("remotes")
library(MLmetrics)

UoW_energy<-read_excel("UoW_load.xlsx", sheet = "Sheet1")
twoInput<-read_excel("UoW_load.xlsx", sheet = "Sheet2")
threeInput<-read_excel("UoW_load.xlsx", sheet = "Sheet3")
fourInput<-read_excel("UoW_load.xlsx", sheet = "Sheet4")

fourInput2<-read_excel("UoW_load.xlsx", sheet = "Sheet5")

NARX1<-read_excel("UoW_load.xlsx", sheet = "NARX1")
NARX2<-read_excel("UoW_load.xlsx", sheet = "NARX2")

```





```{r}
normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}



threeInput_norm<-as.data.frame(lapply(threeInput,normalize))

twoInput_norm<-as.data.frame(lapply(twoInput,normalize))

fourInput_norm<-as.data.frame(lapply(fourInput,normalize))

fourInput2_norm<-as.data.frame(lapply(fourInput2,normalize))

NARX1_norm<-as.data.frame(lapply(NARX1, normalize))

NARX2_norm<-as.data.frame(lapply(NARX2, normalize))






```


```{r}
threeInput_train<-threeInput_norm[1:427,]
threeInput_test<-threeInput_norm[428:497,]

twoInput_train<-twoInput_norm[1:428,]
twoInput_test<-twoInput_norm[429:498,]


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput2_train<-fourInput2_norm[1:422,]
fourInput2_test<-fourInput2_norm[423:492,]

NARX1_train<-NARX1_norm[1:427,]
NARX1_test<-NARX1_norm[428:497,]

NARX2_train<-NARX2_norm[1:426,]
NARX2_test<-NARX2_norm[429:498,]
```



### 4 input2 h1 24 h2 6

```{r}
set.seed(12345)
fourInput2Model.h1.24.h2.6.TRUE.nn<-neuralnet(tPlus1~tMinus7+tMinus2+tMinus1+t,data = fourInput2_train,hidden = c(24,6),act.fct = "logistic",linear.output = TRUE)

plot(fourInput2Model.h1.24.h2.6.TRUE.nn, rep = "best")

fourInput2Model.h1.24.h2.6.TRUE.nn_Result<-compute(fourInput2Model.h1.24.h2.6.TRUE.nn,fourInput2_test[1:4])


predicted_tomorrow<-fourInput2Model.h1.24.h2.6.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput2_test$tPlus1)


fourInput2_train<-fourInput2_norm[1:422,]
fourInput2_test<-fourInput2_norm[423:492,]

fourInput2_train_original<-as.data.frame(fourInput2[1:422,"tPlus1"])


fourInput2_test_original<-as.data.frame(fourInput2[423:492,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput2_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput2_train_original)
#tomorrow_max


head(fourInput2_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

plot(data.frame(fourInput2_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput2_test_original, tomorrow_pred)
final_result
```



```{r}
set.seed(12345)
fourInput2Model.h1.24.h2.6.TRUE.nn<-neuralnet(tPlus1~tMinus7+tMinus2+tMinus1+t,data = fourInput2_train,hidden = c(22,5),act.fct = "logistic",linear.output = TRUE)

plot(fourInput2Model.h1.24.h2.6.TRUE.nn, rep = "best")

fourInput2Model.h1.24.h2.6.TRUE.nn_Result<-compute(fourInput2Model.h1.24.h2.6.TRUE.nn,fourInput2_test[1:4])


predicted_tomorrow<-fourInput2Model.h1.24.h2.6.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput2_test$tPlus1)


fourInput2_train<-fourInput2_norm[1:422,]
fourInput2_test<-fourInput2_norm[423:492,]

fourInput2_train_original<-as.data.frame(fourInput2[1:422,"tPlus1"])


fourInput2_test_original<-as.data.frame(fourInput2[423:492,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput2_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput2_train_original)
#tomorrow_max


head(fourInput2_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

plot(data.frame(fourInput2_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput2_test_original, tomorrow_pred)
final_result
```




### 4 input h1 22 h2 8 

```{r}
set.seed(12345)
fourInput2Model.h1.22.h2.8.TRUE.nn<-neuralnet(tPlus1~tMinus7+tMinus2+tMinus1+t,data = fourInput2_train,hidden = c(9),act.fct = "logistic",linear.output = TRUE)

plot(fourInput2Model.h1.22.h2.8.TRUE.nn,rep = "best")

fourInput2Model.h1.22.h2.8.TRUE.nn_Result<-compute(fourInput2Model.h1.22.h2.8.TRUE.nn,fourInput2_test[1:4])


predicted_tomorrow<-fourInput2Model.h1.22.h2.8.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput2_test$tPlus1)


fourInput2_train<-fourInput2_norm[1:422,]
fourInput2_test<-fourInput2_norm[423:492,]

fourInput2_train_original<-as.data.frame(fourInput2[1:422,"tPlus1"])


fourInput2_test_original<-as.data.frame(fourInput2[423:492,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput2_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput2_train_original)
#tomorrow_max


head(fourInput2_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

plot(data.frame(fourInput2_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput2_test_original, tomorrow_pred)
final_result
```







### 4 input model 2 with hidden layer1 = 19 hidden layer 2 = 6


```{r}

set.seed(12345)

fourInput2Model.h1.19.h2.6.TRUE.nn<-neuralnet(tPlus1~tMinus7+tMinus2+tMinus1+t,data = fourInput2_train,hidden = c(19,6),act.fct = "logistic",linear.output = TRUE)

plot(fourInput2Model.h1.19.h2.6.TRUE.nn,rep = "best")


fourInput2Model.h1.19.h2.6.TRUE.nn_Result<-compute(fourInput2Model.h1.19.h2.6.TRUE.nn,fourInput2_test[1:4])


predicted_tomorrow<-fourInput2Model.h1.19.h2.6.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput2_test$tPlus1)


fourInput2_train<-fourInput2_norm[1:422,]
fourInput2_test<-fourInput2_norm[423:492,]

fourInput2_train_original<-as.data.frame(fourInput2[1:422,"tPlus1"])


fourInput2_test_original<-as.data.frame(fourInput2[423:492,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput2_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput2_train_original)
#tomorrow_max


head(fourInput2_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

plot(data.frame(fourInput2_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput2_test_original, tomorrow_pred)
final_result

```


### 4 input model 2 with hidden layer1 = 13 hidden layer 2 = 3
```{r}
set.seed(12345)
fourInput2Model.h1.13.h2.3.TRUE.nn<-neuralnet(tPlus1~tMinus7+tMinus2+tMinus1+t,data = fourInput2_train,hidden = c(13,3),act.fct = "logistic",linear.output = TRUE)

plot(fourInput2Model.h1.13.h2.3.TRUE.nn)

fourInput2Model.h1.13.h2.3.TRUE.nn_Result<-compute(fourInput2Model.h1.13.h2.3.TRUE.nn,fourInput2_test[1:4])


predicted_tomorrow<-fourInput2Model.h1.13.h2.3.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput2_test$tPlus1)


fourInput2_train<-fourInput2_norm[1:422,]
fourInput2_test<-fourInput2_norm[423:492,]

fourInput2_train_original<-as.data.frame(fourInput2[1:422,"tPlus1"])


fourInput2_test_original<-as.data.frame(fourInput2[423:492,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput2_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput2_train_original)
#tomorrow_max


head(fourInput2_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput2_test_original)))

plot(data.frame(fourInput2_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput2_test_original, tomorrow_pred)
final_result
```



## 4 inputs t-3 ,t-2 ,t-1 ,t


### 4 input h1 12
```{r}

set.seed(12345)
fourInputModel.h1.12.TRUE.nn<-neuralnet(tPlus1~tMinus3+tMinus2+tMinus1+t,
                                        data = fourInput_train,hidden = c(12),
                                        act.fct = "logistic",linear.output = TRUE)
plot(fourInputModel.h1.12.TRUE.nn)


fourInputModel.h1.12.TRUE.nn_Result<-compute(fourInputModel.h1.12.TRUE.nn,fourInput_test[1:4])


predicted_tomorrow<-fourInputModel.h1.12.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput_test$tPlus1)


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput_train_original<-as.data.frame(fourInput[1:426,"tPlus1"])


fourInput_test_original<-as.data.frame(fourInput[427:496,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput_train_original)
#tomorrow_max


head(fourInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

plot(data.frame(fourInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput_test_original, tomorrow_pred)
final_result


```

'### 4 input h1 12 h2 6

```{r}

set.seed(12345)
fourInputModel.h1.12.h2.6.TRUE.nn<-neuralnet(tPlus1~tMinus3+tMinus2+tMinus1+t,
                                              data = fourInput_train,hidden = c(12,6),
                                              act.fct = "logistic",linear.output = TRUE)
plot(fourInputModel.h1.12.h2.6.TRUE.nn, rep="best")



fourInputModel.h1.12.h2.6.TRUE.nn_Result<-compute(fourInputModel.h1.12.h2.6.TRUE.nn,fourInput_test[1:4])


predicted_tomorrow<-fourInputModel.h1.12.h2.6.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput_test$tPlus1)


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput_train_original<-as.data.frame(fourInput[1:426,"tPlus1"])


fourInput_test_original<-as.data.frame(fourInput[427:496,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput_train_original)
#tomorrow_max


head(fourInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

plot(data.frame(fourInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput_test_original, tomorrow_pred)
final_result





```




```{r}
set.seed(12345)
fourInputModel.h1.12.TRUE.nn<-neuralnet(tPlus1~tMinus3+tMinus2+tMinus1+t,
                                        data = fourInput_train,hidden = c(12),
                                        act.fct = "logistic",linear.output = TRUE)
plot(fourInputModel.h1.12.TRUE.nn)


fourInputModel.h1.12.TRUE.nn_Result<-compute(fourInputModel.h1.12.TRUE.nn,fourInput_test[1:4])


predicted_tomorrow<-fourInputModel.h1.12.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput_test$tPlus1)


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput_train_original<-as.data.frame(fourInput[1:426,"tPlus1"])


fourInput_test_original<-as.data.frame(fourInput[427:496,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput_train_original)
#tomorrow_max


head(fourInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

plot(data.frame(fourInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput_test_original, tomorrow_pred)
final_result


```

'### 4 input h1 12 h2 6

```{r}

set.seed(12345)
fourInputModel.h1.12.h2.6.TRUE.nn<-neuralnet(tPlus1~tMinus3+tMinus2+tMinus1+t,
                                              data = fourInput_train,hidden = c(18),
                                              act.fct = "logistic",linear.output = TRUE)
plot(fourInputModel.h1.12.h2.6.TRUE.nn, rep="best")



fourInputModel.h1.12.h2.6.TRUE.nn_Result<-compute(fourInputModel.h1.12.h2.6.TRUE.nn,fourInput_test[1:4])


predicted_tomorrow<-fourInputModel.h1.12.h2.6.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput_test$tPlus1)


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput_train_original<-as.data.frame(fourInput[1:426,"tPlus1"])


fourInput_test_original<-as.data.frame(fourInput[427:496,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput_train_original)
#tomorrow_max


head(fourInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

plot(data.frame(fourInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput_test_original, tomorrow_pred)
final_result
```

### 4 input h1 18 h2 4
```{r}

set.seed(12345)
fourInputModel.h1.18.h2.4.TRUE.nn<-neuralnet(tPlus1~tMinus3+tMinus2+tMinus1+t,
                                             data = fourInput_train,hidden = c(18,4),
                                             act.fct = "logistic",linear.output = TRUE)

plot(fourInputModel.h1.18.h2.4.TRUE.nn)





fourInputModel.h1.18.h2.4.TRUE.nn_Result<-compute(fourInputModel.h1.18.h2.4.TRUE.nn,fourInput_test[1:4])


predicted_tomorrow<-fourInputModel.h1.18.h2.4.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput_test$tPlus1)


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput_train_original<-as.data.frame(fourInput[1:426,"tPlus1"])


fourInput_test_original<-as.data.frame(fourInput[427:496,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput_train_original)
#tomorrow_max


head(fourInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

plot(data.frame(fourInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput_test_original, tomorrow_pred)
final_result




```

### 4 input h1 20 h2 9

```{r}
set.seed(12345)
fourInputModel.h1.20.h2.9.TRUE.nn<-neuralnet(tPlus1~tMinus3+tMinus2+tMinus1+t,
                                              data = fourInput_train,hidden = c(20,9),
                                              act.fct = "logistic",linear.output = TRUE)

plot(fourInputModel.h1.20.h2.9.TRUE.nn, rep = "best")


fourInputModel.h1.20.h2.9.TRUE.nn_Result<-compute(fourInputModel.h1.20.h2.9.TRUE.nn,fourInput_test[1:4])


predicted_tomorrow<-fourInputModel.h1.20.h2.9.TRUE.nn_Result$net.result

cor(predicted_tomorrow,fourInput_test$tPlus1)


fourInput_train<-fourInput_norm[1:426,]
fourInput_test<-fourInput_norm[427:496,]

fourInput_train_original<-as.data.frame(fourInput[1:426,"tPlus1"])


fourInput_test_original<-as.data.frame(fourInput[427:496,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(fourInput_train_original)
#tomorrow_min

tomorrow_max<-max(fourInput_train_original)
#tomorrow_max


head(fourInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(fourInput_test_original)))

plot(data.frame(fourInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(fourInput_test_original, tomorrow_pred)
final_result



```




## 3 input model t-2, t-1, t

### 2 input h1 10

```{r}
set.seed(12345)
threeInputModel.h1.10.TRUE.nn<-neuralnet(tPlus1~tMinus2+tMinus1+t,
                                        data = threeInput_train,hidden = c(10),
                                        act.fct = "logistic",linear.output = TRUE)

plot(threeInputModel.h1.10.TRUE.nn, rep= "best")


threeInputModel.h1.10.TRUE.nn_Result<-compute(threeInputModel.h1.10.TRUE.nn,threeInput_test[1:3])


predicted_tomorrow<-threeInputModel.h1.10.TRUE.nn_Result$net.result

cor(predicted_tomorrow,threeInput_test$tPlus1)


threeInput_train<-threeInput_norm[1:427,]
threeInput_test<-threeInput_norm[428:497,]


threeInput_train_original<-as.data.frame(threeInput[1:427,"tPlus1"])


threeInput_test_original<-as.data.frame(threeInput[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(threeInput_train_original)
#tomorrow_min

tomorrow_max<-max(threeInput_train_original)
#tomorrow_max


head(threeInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

plot(data.frame(threeInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(threeInput_test_original, tomorrow_pred)
final_result



```



```{r}
set.seed(12345)
threeInputModel.h1.10.TRUE.nn<-neuralnet(tPlus1~tMinus2+tMinus1+t,
                                        data = threeInput_train,hidden = c(9),
                                        act.fct = "logistic",linear.output = TRUE)

plot(threeInputModel.h1.10.TRUE.nn, rep= "best")


threeInputModel.h1.10.TRUE.nn_Result<-compute(threeInputModel.h1.10.TRUE.nn,threeInput_test[1:3])


predicted_tomorrow<-threeInputModel.h1.10.TRUE.nn_Result$net.result

cor(predicted_tomorrow,threeInput_test$tPlus1)


threeInput_train<-threeInput_norm[1:427,]
threeInput_test<-threeInput_norm[428:497,]


threeInput_train_original<-as.data.frame(threeInput[1:427,"tPlus1"])


threeInput_test_original<-as.data.frame(threeInput[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(threeInput_train_original)
#tomorrow_min

tomorrow_max<-max(threeInput_train_original)
#tomorrow_max


head(threeInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

plot(data.frame(threeInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(threeInput_test_original, tomorrow_pred)
final_result

```

### h1 10 h2 5

```{r}
set.seed(12345)
threeInputModel.h1.10.h2.5.TRUE.nn<-neuralnet(tPlus1~tMinus2+tMinus1+t,
                                               data = threeInput_train,hidden = c(10,5),
                                               act.fct = "logistic",linear.output = TRUE)
plot(threeInputModel.h1.10.h2.5.TRUE.nn, rep = "best")



threeInputModel.h1.10.h2.5.TRUE.nn_Result<-compute(threeInputModel.h1.10.h2.5.TRUE.nn,threeInput_test[1:3])


predicted_tomorrow<-threeInputModel.h1.10.h2.5.TRUE.nn_Result$net.result

cor(predicted_tomorrow,threeInput_test$tPlus1)


threeInput_train<-threeInput_norm[1:427,]
threeInput_test<-threeInput_norm[428:497,]


threeInput_train_original<-as.data.frame(threeInput[1:427,"tPlus1"])


threeInput_test_original<-as.data.frame(threeInput[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(threeInput_train_original)
#tomorrow_min

tomorrow_max<-max(threeInput_train_original)
#tomorrow_max


head(threeInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

plot(data.frame(threeInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(threeInput_test_original, tomorrow_pred)
final_result

```
### 3input h1 24 h2 8

```{r}
set.seed(12345)

threeInputModel.h1.24.h2.8.TRUE.nn<-neuralnet(tPlus1~tMinus2+tMinus1+t,
                                               data = threeInput_train,hidden = c(24,8),
                                               act.fct = "logistic",linear.output = TRUE)

plot(threeInputModel.h1.24.h2.8.TRUE.nn, rep = "best")



threeInputModel.h1.24.h2.8.TRUE.nn_Result<-compute(threeInputModel.h1.24.h2.8.TRUE.nn,threeInput_test[1:3])


predicted_tomorrow<-threeInputModel.h1.24.h2.8.TRUE.nn_Result$net.result

cor(predicted_tomorrow,threeInput_test$tPlus1)


threeInput_train<-threeInput_norm[1:427,]
threeInput_test<-threeInput_norm[428:497,]


threeInput_train_original<-as.data.frame(threeInput[1:427,"tPlus1"])


threeInput_test_original<-as.data.frame(threeInput[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(threeInput_train_original)
#tomorrow_min

tomorrow_max<-max(threeInput_train_original)
#tomorrow_max


head(threeInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

plot(data.frame(threeInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(threeInput_test_original, tomorrow_pred)
final_result



```
### 3 input h1 23 h2 3


```{r}
set.seed(12345)
threeInputModel.h1.23.h2.3.TRUE.nn<-neuralnet(tPlus1~tMinus2+tMinus1+t,
                                              data = threeInput_train,hidden = c(23,3),
                                              act.fct = "logistic",linear.output = TRUE)

plot(threeInputModel.h1.23.h2.3.TRUE.nn)


threeInputModel.h1.23.h2.3.TRUE.nn_Result<-compute(threeInputModel.h1.23.h2.3.TRUE.nn,threeInput_test[1:3])


predicted_tomorrow<-threeInputModel.h1.23.h2.3.TRUE.nn_Result$net.result

cor(predicted_tomorrow,threeInput_test$tPlus1)


threeInput_train<-threeInput_norm[1:427,]
threeInput_test<-threeInput_norm[428:497,]


threeInput_train_original<-as.data.frame(threeInput[1:427,"tPlus1"])


threeInput_test_original<-as.data.frame(threeInput[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(threeInput_train_original)
#tomorrow_min

tomorrow_max<-max(threeInput_train_original)
#tomorrow_max


head(threeInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(threeInput_test_original)))

plot(data.frame(threeInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(threeInput_test_original, tomorrow_pred)
final_result




```

## 2 input t and t-1


```{r}
set.seed(12345)
twoInput_model.h1.10.h2.8.nn<-neuralnet(tPlus1~t+tMinus1,data = twoInput_train, hidden = c(10,8),act.fct = "logistic",linear.output = TRUE)

plot(twoInput_model.h1.10.h2.8.nn, rep = "best") 

twoInput_model.h1.10.h2.8.nn_Result<-compute(twoInput_model.h1.10.h2.8.nn,twoInput_test[1:2])


predicted_tomorrow<-twoInput_model.h1.10.h2.8.nn_Result$net.result

cor(predicted_tomorrow,twoInput_test$tPlus1)


twoInput_train<-twoInput_norm[1:428,]
twoInput_test<-twoInput_norm[429:498,]


twoInput_train_original<-as.data.frame(twoInput[1:428,"tPlus1"])


twoInput_test_original<-as.data.frame(twoInput[429:498,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(twoInput_train_original)
#tomorrow_min

tomorrow_max<-max(twoInput_train_original)
#tomorrow_max


head(twoInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))

plot(data.frame(twoInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(twoInput_test_original, tomorrow_pred)
final_result



```
```{r}
set.seed(12345)
twoInput_model.h1.15.h2.4.nn<-neuralnet(tPlus1~t+tMinus1,data = twoInput_train, hidden = c(15,4),act.fct = "logistic",linear.output = TRUE)

plot(twoInput_model.h1.15.h2.4.nn, rep = "best") 

twoInput_model.h1.15.h2.4.nn_Result<-compute(twoInput_model.h1.15.h2.4.nn,twoInput_test[1:2])


predicted_tomorrow<-twoInput_model.h1.15.h2.4.nn_Result$net.result

cor(predicted_tomorrow,twoInput_test$tPlus1)


twoInput_train<-twoInput_norm[1:428,]
twoInput_test<-twoInput_norm[429:498,]


twoInput_train_original<-as.data.frame(twoInput[1:428,"tPlus1"])


twoInput_test_original<-as.data.frame(twoInput[429:498,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(twoInput_train_original)
#tomorrow_min

tomorrow_max<-max(twoInput_train_original)
#tomorrow_max


head(twoInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
tomorrow_pred 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))

plot(data.frame(twoInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(twoInput_test_original, tomorrow_pred)
final_result
```
```{r}
set.seed(12345)
twoInput_model.h1.12.nn<-neuralnet(tPlus1~t+tMinus1,data = twoInput_train, hidden = c(12),act.fct = "logistic",linear.output = TRUE)

plot(twoInput_model.h1.12.nn, rep = "best") 

twoInput_model.h1.12.nn_Result<-compute(twoInput_model.h1.12.nn,twoInput_test[1:2])


predicted_tomorrow<-twoInput_model.h1.12.nn_Result$net.result

cor(predicted_tomorrow,twoInput_test$tPlus1)


twoInput_train<-twoInput_norm[1:428,]
twoInput_test<-twoInput_norm[429:498,]


twoInput_train_original<-as.data.frame(twoInput[1:428,"tPlus1"])


twoInput_test_original<-as.data.frame(twoInput[429:498,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(twoInput_train_original)
#tomorrow_min

tomorrow_max<-max(twoInput_train_original)
#tomorrow_max


head(twoInput_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)
 


RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))  
MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(twoInput_test_original)))

plot(data.frame(twoInput_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(twoInput_test_original, tomorrow_pred)
final_result

```


```{r}
set.seed(12345)
NARX1.model<-neuralnet(tPlus1~tMinus2+tMinus1+t+t9+t10,data = NARX1_train,hidden = c(12,2),act.fct = "logistic",linear.output = TRUE)

plot(NARX1.model, rep = "best")

NARX1.model_Result<-compute(NARX1.model,NARX1_test[1:5])


predicted_tomorrow<-NARX1.model_Result$net.result

cor(predicted_tomorrow,NARX1_test$tPlus1)

NARX1_train<-NARX1_norm[1:427,]
NARX1_test<-NARX1_norm[428:497,]



NARX1_train_original<-as.data.frame(NARX1[1:427,"tPlus1"])


NARX1_test_original<-as.data.frame(NARX1[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(NARX1_train_original)
#tomorrow_min

tomorrow_max<-max(NARX1_train_original)
#tomorrow_max


head(NARX1_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)



RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))  

MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))

plot(data.frame(NARX1_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(NARX1_test_original, tomorrow_pred)
final_result

```
```{r}
set.seed(12345)
NARX1.model.h1.24.h2.6.nn<-neuralnet(tPlus1~tMinus2+tMinus1+t+t9+t10,data = NARX1_train,hidden = c(8),act.fct = "logistic",linear.output = TRUE)

plot(NARX1.model, rep = "best")

NARX1.model.h1.24.h2.6.nn_Result<-compute(NARX1.model.h1.24.h2.6.nn,NARX1_test[1:5])


predicted_tomorrow<-NARX1.model.h1.24.h2.6.nn_Result$net.result

cor(predicted_tomorrow,NARX1_test$tPlus1)

NARX1_train<-NARX1_norm[1:427,]
NARX1_test<-NARX1_norm[428:497,]



NARX1_train_original<-as.data.frame(NARX1[1:427,"tPlus1"])


NARX1_test_original<-as.data.frame(NARX1[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(NARX1_train_original)
#tomorrow_min

tomorrow_max<-max(NARX1_train_original)
#tomorrow_max


head(NARX1_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)



RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))  

MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))

plot(data.frame(NARX1_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(NARX1_test_original, tomorrow_pred)
final_result

```



```{r}

set.seed(12345)
NARX2.model<-neuralnet(tPlus1~t10+tMinus1+t,data = NARX2_train,hidden = c(21,4),act.fct = "logistic",linear.output = TRUE)

plot(NARX2.model, rep = "best")

NARX2.model_Result<-compute(NARX2.model,NARX2_test[1:3])


predicted_tomorrow<-NARX2.model_Result$net.result

cor(predicted_tomorrow,NARX2_test$tPlus1)


NARX2_train<-NARX2_norm[1:426,]
NARX2_test<-NARX2_norm[429:498,]



NARX2_train_original<-as.data.frame(NARX2[1:426,"tPlus1"])


NARX2_test_original<-as.data.frame(NARX2[429:498,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(NARX2_train_original)
#tomorrow_min

tomorrow_max<-max(NARX2_train_original)
#tomorrow_max


head(NARX2_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)



RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX2_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX2_test_original)))  

MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX2_test_original)))

plot(data.frame(NARX2_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(NARX2_test_original, tomorrow_pred)
final_result

```


```{r}
set.seed(12345)
NARX1.model<-neuralnet(tPlus1~tMinus2+tMinus1+t+t9+t10,data = NARX1_train,hidden = c(15),act.fct = "logistic",linear.output = TRUE)

plot(NARX1.model, rep = "best")

NARX1.model_Result<-compute(NARX1.model,NARX1_test[1:5])


predicted_tomorrow<-NARX1.model_Result$net.result

cor(predicted_tomorrow,NARX1_test$tPlus1)

NARX1_train<-NARX1_norm[1:427,]
NARX1_test<-NARX1_norm[428:497,]



NARX1_train_original<-as.data.frame(NARX1[1:427,"tPlus1"])


NARX1_test_original<-as.data.frame(NARX1[428:497,"tPlus1"])
#twoInput_test_original

tomorrow_min<-min(NARX1_train_original)
#tomorrow_min

tomorrow_max<-max(NARX1_train_original)
#tomorrow_max


head(NARX1_train_original)

unnormalize <- function(x, min, max) { 
  return( (max - min)*x + min )
}


tomorrow_pred <- unnormalize(predicted_tomorrow, tomorrow_min, tomorrow_max)



RMSE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))

MAE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))  

MAPE(as.numeric(unlist(tomorrow_pred)),as.numeric(unlist(NARX1_test_original)))

plot(data.frame(NARX1_test_original, tomorrow_pred) ,col='red',main='Real vs predicted NN',pch=18,cex=0.7)
abline(0,1,lwd=2)


final_result <- cbind(NARX1_test_original, tomorrow_pred)
final_result

```

## Discussion of the meaning of these stat. indices 


